PANCHANGE_data_preprocessing

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
moved missigness in the place with the questionnaires

@@

>>>>

# GAD missingness

## baseline
```{r GAD baseline missingness}
coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
  mutate(
    na_per_person_gad_base =         # variable for NA per person
      rowSums(                       
        is.na(.[gad.items_base])
      )
  )

coping.glad.gad.raw.id %>%
  freq(na_per_person_gad_base, cumul = F) #have a look at the frequency
```

We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
```{r GAD base missingness 8 items}
coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
  mutate(
    gad.missing_only_suicide_item_base = 
      if_else(
        condition = na_per_person_gad_base == 1 & 
          is.na(gad.dead_hurting_thoughts_base_numeric), 
        true = 1,
        false = 0,
        missing = NA_real_
      )
  )

coping.glad.gad.raw.id %>%
  freq(gad.missing_only_suicide_item_base,
       cumul = F)
```

## retrospective
```{r GAD retrospective missingness}
coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
  mutate(
    na_per_person_gad_retro =         # variable for NA per person
      rowSums(
        is.na(.[gad.items_retro])
      )
  )

coping.glad.gad.raw.id %>%
  freq(na_per_person_gad_retro, cumul = F) #have a look at the frequency
```

```{r GAD retro missingness 8 items}
coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
  mutate(
    gad.missing_only_suicide_item_retro = 
      if_else(
        condition = na_per_person_gad_retro == 1 & 
          is.na(gad.dead_hurting_thoughts_retro_numeric), 
        true = 1,
        false = 0,
        missing = NA_real_
      )
  )

coping.glad.gad.raw.id %>%
  freq(gad.missing_only_suicide_item_retro,
       cumul = F)
```

@@

# PHQ missigness
